---
title: "Diagnostic Plots"
subtitle: "Self-talk interventions and sport/motor performance: An updated systematic review and Bayesian meta-analysis"
author: "Hannah Corcoran, James Steele"
format:
  pdf:
    documentclass: report
    toc: false
    number-sections: false
    highlight-style: github
    fig-width: 10
    fig-height: 10
---
# Main Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_main_model)

rhat_main_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_main_model)

trace_plot_main_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_main_model)

pp_check_main_model

```

# Motor Demands Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_motor_demands_model)

rhat_motor_demands_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_motor_demands_model)

trace_plot_motor_demands_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_motor_demands_model)

pp_check_motor_demands_model

```

# Participant Group Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_participant_group_model)

rhat_participant_group_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_participant_group_model)

trace_plot_participant_group_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_participant_group_model)

pp_check_participant_group_model

```

# Self-Talk Content Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_selftalk_content_model)

rhat_selftalk_content_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_selftalk_content_model)

trace_plot_selftalk_content_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_selftalk_content_model)

pp_check_selftalk_content_model

```

# Matching Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_matching_model)

rhat_matching_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_matching_model)

trace_plot_matching_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_matching_model)

pp_check_matching_model

```

# task_novelty Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_task_novelty_model)

rhat_task_novelty_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_task_novelty_model)

trace_plot_task_novelty_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_task_novelty_model)

pp_check_task_novelty_model

```

# Cue Selection Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_cue_selection_model)

rhat_cue_selection_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_cue_selection_model)

trace_plot_cue_selection_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_cue_selection_model)

pp_check_cue_selection_model

```

# Overtness Selection Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_overtness_selection_model)

rhat_overtness_selection_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_overtness_selection_model)

trace_plot_overtness_selection_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_overtness_selection_model)

pp_check_overtness_selection_model

```

# Training Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_training_model)

rhat_training_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_training_model)

trace_plot_training_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_training_model)

pp_check_training_model

```

# Study Design Model

## $\hat{R}$

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(rhat_study_design_model)

rhat_study_design_model 


```

## Trace plots

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(trace_plot_study_design_model)

trace_plot_study_design_model

```

## Posterior predictive check

```{r,message=FALSE,warning=FALSE,echo=FALSE}

targets::tar_load(pp_check_study_design_model)

pp_check_study_design_model

```
